%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer (Part Time)} % Job title
    {Archlet AG} % Organization
    {Z\"urich, Switzerland} % Location
    {Sep. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed and maintained a web application with Kubernetes on Microsoft Azure.}
        \item {Maintained business logic engine in Python and deployment scripts using Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace*{-0.15cm}  
\cventry
    {Data Scientist} % Job title
    {} % Organization
    {} % Location
    {May 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Python optimization engine making extensive use of packages such as Pandas, Numpy and SQLAlchemy.}
        \item {Designed the architecture of a distributed and containerized cloud-based web application.}
        \item {Collaborated with an external agency on the development of the user interface.}
        \item {Deployed a proof of concept application on Microsoft Azure using Docker Swarm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems and Control Engineering Intern} % Job title
    {Verity Studios AG} % Organization
    {Z\"urich, Switzerland} % Location
    {May. 2017 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on control and estimation algorithms for swarms of quadcopters in C++.}
        \item {Evaluated flight data using Python and improved drone production pipeline.}
        \item {Developped offboard user interface applications implemented in C++.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Radio Frequencies Engineer} % Job title
    {UTIAS Space Flight Laboratories} % Organization
    {Toronto, Canada} % Location
    {Jun. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and simulated early prototypes of a deployable antenna mounted on the NORSAT-2 maritime communications satellite.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
